Token-level author diarization using clustering of stylistic contexts

### 2017-05-31 paper/paper.tex
no message

\section{Author diarization and intrinsic plagiarism detetion}
% describe the problem
% define formally: document, segmentation, segment, author assignement (label)
% define evaluation metrics

@@

Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$. Here $\Delta$ is the tokenized document domain as defined in section ((((((($\circ$))))))). $\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively. $n_b$ and $n_d$ can either be fixed or depend on the document being processed. $C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.

@@

The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) features are extracted for all tokens and their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.

@@

Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$. Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.

>>>>

\section{Author diarization and intrinsic plagiarism detetion} \label{sec:author-diraization}
% describe the problem
% define formally: document, segmentation, segment, author assignement (label)
% define evaluation metrics

@@

Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$. Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization}. $\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively. $n_b$ and $n_t$ can either be fixed or depend on the document being processed. $C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.

@@

The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) for all tokens, features are extracted from their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.

@@

Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$, i.e. we want to maximize segregation and compactness of clusters consisting of transformed feature vectors labeled with their true author labels. Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$. We define the following loss in order to optimize the transformation $T$ for clusterability:
\begin{equation}
	L = L_\mathrm{c} + L_\mathrm{s},
\end{equation}
where $L_\mathrm{c}$ is the \emph{compactness loss} which is proportional to the average variance of groups and $L_\mathrm{s}$ the \emph{segregation loss}.
\begin{align}
	L_\mathrm{c} &= \\
	L_\mathrm{s} &= 
\end{align}
